{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Missing term in Equations added

	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

	{\color{orange} For the last equation, shouldn't it be approx including following equations regarding truncation error term? or delta times delta is so small that we can neglect(maybe not true)..?} In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
	\end{equation}

	And we can define the following objects:
		\begin{align}
			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] 
			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) 
			& \delta_{\nu, m}^L(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
		\end{align}

>>>>

	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
		\begin{split}
			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
		\end{split}
	\end{equation}

	And we can define the following objects:
		\begin{align}
			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] 
			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} d_{k}^m \phi_{k}(t) 
			& \delta_{\nu, m}^L(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
		\end{align}
